Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-20 article.tex
small wording

If the undirected network is perfectly inferred, it would already yield
high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
to infer edge directivity is likely to be counter-productive or yield
small gain.
By contrast, the same experiment with AUPRC would yield
to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
correctly directivity would be more rewarding in AUPRC term.
Interestingly, methods that takes into account directivity, namely GTE and
GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
(see GTE and GTE(undirected) in Figure \ref{fig:curves}
\textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
especially pr-curve.}).
Trying to detect the link direction is more penalizing than rewarding.

>>>>

If the undirected network is perfectly inferred, it would already yield
high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
to infer edge directivity is likely to be counter-productive or yield
small gain.
By contrast, the same experiment with AUPRC would yield
to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
correctly directivity would be more rewarding in AUPRC term.
Interestingly, methods that takes into account directivity, namely GTE and
GENIE3, slightly improve their AUROC and AUPRC by giving the same way to directed edges.
(see GTE and GTE(undirected) in Figure \ref{fig:curves}
\textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
especially pr-curve.}).
Trying to detect the link direction is more penalizing than rewarding.
